### 2019-07-23 README.Rmd

[![Travis-CI Build Status](https://travis-ci.org/sahirbhatnagar/cbpaper.svg?branch=master)](https://travis-ci.org/sahirbhatnagar/cbpaper)

>>>>

[![Binder](http://mybinder.org/badge.svg)](http://beta.mybinder.org/v2/gh/sahirbhatnagar/cbpaper/master?urlpath=rstudio)  
[![Travis-CI Build Status](https://travis-ci.org/sahirbhatnagar/cbpaper.svg?branch=master)](https://travis-ci.org/sahirbhatnagar/cbpaper)
